Interval Probability and Measurement for Fuzzy Quantum Theories

### 2016-08-20 prob.tex
prob.tex \section{... Then?} Added...

>>>>

\section{... Then?}

\yutsung{Because theorem~\ref{def:EmptyCoreQuantumInterval-valuedProbability}
gives a negative result, our original plan was to put the Mermin v.s.
Meyer debate here, and move on to the discrete quantum probability
measure. Then, discrete real-valued quantum probability measures are
expected to fail because of John's proof, and we hope discrete interval-valued
quantum probability measure can work in some sense?

I just want to confirm whether we want to keep our original plan to
move on to the discrete quantum probability measure. Because we don't
really use $\mathbb{C}$ in example~\ref{ex:three-dimensional-three-value},
I could expect example~\ref{ex:three-dimensional-three-value} is
highly likely to serve as an counterexample for discrete interval-valued
quantum probability measure...

Some alternatives:
\begin{enumerate}
\item The importance of Gleason's theorem is that the Born rule could be
deduced from other postulates. If the Gleason's theorem fails, we
may still postulate the Born rule... But why? And this method doesn't
really solve the problem in discrete quantum theories because there
is no original Born rule...
\item We may give up the idea of representing a quantum state as a density
matrix. Actually, quantum probability people think quantum states
are functions~\cite{Maassen2010,Swart2013,Hamhalter2013}, and Emanuel
(Manny) Knill starts from C{*}-algebra when we talk about quantum
measurement. Maybe reasoning quantum states as a function in every
quantum phenomena is doable?
\end{enumerate}
}
